### 2022-07-30 thesis/realtime.tex
Second draft of thesis finished

Recall from Sections \ref{sec:bernstein} and \ref{sec:static} that computing the Bernstein coefficients and taking their maximum and minimum coefficients is tantamount to bounding the solutions to non-linear optimization problems of the form presented in Equation \ref{eq:maxalpha}. As the degrees of the polynomial predicates and dimensions of the system grow, the number of Bernstein coefficients also grows in exponential order. This is evident from the Bernstein coefficient formula defined in Equation \ref{eq:bernstein_coeff}.

@@

\begin{description}
\item[Parition Domain into Grid:] We first partition the domain into grid cells of equal dimension. Naturally the entire domain is infinite, so we must restrict the domain into bounded box of sufficiently large dimensions. This box must bound the reachable set computed for a finite number of steps forward. These grid cells will act as constraints to feed into our generator representation.
\item[Initialize Generator Representation:] For each of the cells computed in the previous step, we set the anchor vertex and generator vector components to their corresponding grid cell dimension. In other words, we constrain the parallelotope to be contained within the cell through the generator representation. Formally speaking, suppose we have a grid cell $G$ in $n$-dimensional real vector space $\reals^n$ of the form $G = [l_1,u_1] \times [l_2, u_2] \times \cdots [l_n \times u_n]$. To constrain our parallelotope $P = \langle a, g_1, \cdots, g_n\rangle$ to be contained within $g$, it suffices to set the component variables such that $a, g_1, \cdots, g_n \in G$. For example, to set $a \in G$, the constraints should be initialized as below:
\begin{align}
\label{eq:gen_var_interval}
  a_1 \gets [l_1,u_1] & & a_2 \gets [l_2, u_2] & & \cdots & & a_n \gets [l_n,u_n]
\end{align}
%
%\begin{align*}
%  a_1 & \in [l_1,u_1] & a_1 & \in [l_2, u_2] & \cdots & & a_n \in [l_n,u_n] \\
%  g_{11} & \in [l_1,u_1] & g_{12} & \in [l_2, u_2] & \cdots&   & g_{1n} \in [l_n,u_n] \\
%  & \vdots & & \vdots &
%\end{align*}
%
In Algorithm \ref{alg:bern_prune}, the procedure responsible returning this assignment is $\ComputeGridRep$.

\item[Perform the Functional Composition:] As stated in Equation \ref{eq:maxalpha}, the non-linear optimization predicate should be $\Lambda_i\cdot f$ for fixed template direction $\Lambda_i$. Under the assignments of the variables according to Equation \ref{eq:gen_var_interval} and interval arithmetic, we have the polynomial $\Lambda_i\cdot(f \circ T_p)$ where the coefficients are \emph{intervals} rather than real values.

\item[Compute Bernstein Coefficient Intervals:] Now with our computed polynomial with interval coefficients, we can compute the Bernstein coefficient intervals using the formula displayed in Equation \ref{eq:bernstein_coeff}. By our initialization scheme above, this computation will yield intervals such that the Bernstein coefficients computed from any parallelotope contained in grid cell $P \subseteq G$ should lie within their respective coefficient intervals. Let $\{\barb_{\boldi}\}_{\boldi \in I_{G,\Lambda_i}}$ be the set of computed coefficient intervals where $I_{G,\Lambda_i}$ is an index of degrees which depend on the grid cell $G$ and template direction $\Lambda_i$. For the sake of clarity, we shall just denote this index set as $I$.

\item[Find the Maximum/Minimum Interval:] Using $\{\barb_{\boldi}\}$, we find the maximum and minimum interval by simply finding the interval which has the largest upper-bound and the interval which has the smallest lower-bound. If $\barb_{\boldi} = [l_\boldi, u_\boldi]$, then
%
\begin{align}
  \mathfrak{I}_{G,\Lambda_i, \max} & = \argmax_{\boldi \in I} u_\boldi \\
  \mathfrak{I}_{G,\Lambda_i, \min} & = \argmin_{\boldi \in I} u_\boldi
\end{align}
%
Note that $\mathfrak{I}_{\max}, \mathfrak{I}_{\min}$ are the degrees of the Bernstein basis monomials whose intervals dominate the others. Additionally, we add all the intervals which overlap with the maximum and minimum intervals:
%
\begin{align}
  \begin{split}
      m_{G,\Lambda_i,\max} & = \{\boldi \in I ~|~ \barb_{\boldi} \cap \barb_{\mathfrak{I}_{\max}} \neq \emptyset \}\\
      m_{G,\Lambda_i,\min} & = \{\boldi \in I ~|~ \barb_{\boldi} \cap \barb_{\mathfrak{I}_{\min}} \neq \emptyset \}
  \end{split}
\end{align}

\item[Store into Lookup Table:] The maximum and minimum intervals and their associated degrees are stored into a lookup table indiced by each grid cell and template direction $\Lambda_i$ in $\Lambda$.
\end{description}

@@

  \begin{tabular}{|c|c|c|c|}
  \hline
  Model & Domain & Initial Set & \# of Grid Cells \\
  \hline
  Vanderpol & $[-3, 3] \times [-3, 3]$ & $[0.001, 0.005]\times [1.995, 2]$ & 1600 \\
  \hline
  SIR & $[0, 1]^3$ & $[0.799,0.8] \times [0.199,0.2] \times 0$ & 100 \\
  \hline
  \end{tabular}
\end{itemize}

\subsection{Discrepancy of Degrees}
This issue arises when we compute the actual maximum and minimum intervals during the pre-computation step. We will demonstrate this phenomenon with the Vanderpol System:

Recall that the generator representation for ptope $P$ would yield the linear transformation $T:[0,1] \rightarrow P$ which looks like $$ T(x,y) = q + g_0*x + g_1*y$$ for an anchor (base) vertex $q$ and two generator vectors $g_0,g_1$.
%
The functional composition with the generator representation would be substituting the symbolic expressions as follows:
%
\begin{align} x & \leftarrow q_0 + g_{00}*x + g_{01}*y \\  y & \leftarrow q_1 + g_{01}*x + g_{11}*y\end{align}
%
The composed polynomial $f \circ T$ will look as follows:
%
\begin{align} (f \circ T)_0 & = (q_1 + g_{01}*x + g_{11}*y \\ (f \circ T)_1 & = (1 - (q_0 + g_{00}*x + g_{01}*y)^2) * (q_1 + g_{01}*x + g_{11}*y) - (q_0 + g_{00}*x + g_{01}*y) \end{align}

If you inspect the polynomial $(f \circ T)_1$, the square times another linear factor of $x,y$ gives us a polynomial of degree $(3,3)$. If calculate the non-linear optimization objective function as: $\Lambda \cdot (f \circ T_P)$ where we set $\Lambda = [0,1]^T$ (i.e the y-axis aligned vector), then the polynomial will be precisely be $(f \circ T)_1$, which has degree $(3,3)$.

However, the following occurs during the reachability algorithm: the actual polynomial computed (that is the polynomial computed naturally during the parallelotope reachability algorithm) actually has lower degree than $(3,3)$. Consider the output below computed with just the axis-aligned parallelotope over the VanderPol model with a grid parition of $40 \times 40$:

%-------------------------
%\input{bern_prune_deg_output}
%-------------------------

We could execute an additional pruning method where we simply discard all of the irrelevant monomial degrees that do not show up during the reachability computation. For instance, we can simply remove all the monomial terms if the term has higher degree than $(2,1)$.

However, we run into a subsequent problem of the following sort: if the grid is fine enough to extract a single dominant maximum or minimum coefficient interval and its corresponding monomial, then this may show up as a degree larger than the relevant total degree. In the first above, the maximum degree is a lone monomial:
%
\begin{verbatim}
      Returned set of Maximum Monom from Lookup Table:

      [((3, 3), 2.18359741950000)]
\end{verbatim}
%
This means that the actual monomial with the maximum Bernstein coefficient:
\begin{verbatim}
        Actual Max Monom Deg: (2, 0)
\end{verbatim}
%
was actually pruned out during the pre-computation phase.
%
What seems to happen quite frequently is that the maximum or minimum intervals and their associated overlaps domaintes the actual degree of the ``true" polynomial computed after functional composition during the reachability computation. For instance,

@@

To summarize, it appears that pre-computing the Bernstein coefficients and the subsequent analysis on their outputted intervals can overly skew the effect of ``non-relevant coefficients". These coefficients can only be pruned once the generator representation of the specific parallelotope is computed and the exact degree of the composed polynomial is determined.

\subsection{Obstacles to Speedups}
Another issue that seems to occur is that parallelotopes which have great overlap with many grid cells yield the full list of Bernstein coefficients. Hence, there is no speedup gained in these cases. Consider the following output for Steps $3-5$:
%-------------------------
%\input{bern_prune_wrapping_error}
%-------------------------

The main point to take here are the printed values of returned set of monomials from the lookup table:
%
\begin{verbatim}
Returned set of Maximum Monom from lookup_table:

         [((0, 1), 2.48598940176842),
         ((1, 2), 2.13075300161303),
         ((2, 1), 2.49645813555339),
         ((3, 1), 2.50156197271691),
         ((0, 2), 2.12608267690468),
         ((2, 2), 2.13534845254406),
         ((1, 0), 2.85178155552809),
         ((3, 2), 2.13986902969777),
         ((1, 3), 1.77023872465550),
         ((1, 1), 2.49126727857056),
         ((0, 3), 1.76617595204093),
         ((2, 0), 2.85756781856273),
         ((3, 0), 2.86325491573606),
         ((2, 3), 1.77423876953473),
         ((3, 3), 1.77817608667862)]
\end{verbatim}
%
From Step 4 onwards, the Lookup table returns the full list of monomials of degree less than $(3,3)$ i.e all the relevant monomials during the pre-computation stage.
%
We tested this even for reachability computations lasting more than 5 steps. The full set of Bernstein coefficients are always returned after a certain step. This is case it would be around step $4$ or $5$.

As the wrapping error becomes worse, so does the utility of our Lookup table and the monomials it returns. A guess is that as the conservativeness of our reachable becomes greater, it overlaps with more cells. Hence, we need to take into account more and more monomials as the reachability algorithm progresses.

Hence, we speculate that the utility of our pruning method hinges on the careful control of the reachable set error. If the error becomes too great, we end of computing all of the coefficients in the end.

>>>>

Recall from Sections \ref{sec:bernstein} and \ref{sec:static} that computing the Bernstein coefficients and taking their maximum and minimum coefficients is tantamount to bounding the solutions to non-linear optimization problems of the form presented in Equation \ref{eq:maxalpha}. As the degrees of the polynomial objective functions described by Equation \ref{eq:maxalpha} and dimensions of the system grow, the number of Bernstein coefficients also grows in exponential order. This is evident from the Bernstein coefficient formula defined in Equation \ref{eq:bernstein_coeff}.

@@

\newcommand\litem[1]{\item{\bfseries #1 \\}}

\begin{enumerate}
\litem{Parition Domain into Grid Cells:} We first partition the domain into grid cells of equal dimension. Naturally the entire domain is infinite, so we must restrict the domain into bounded box of sufficiently large dimensions. This box must bound the reachable set computed for a finite number of steps forward. These grid cells will act as constraints to feed into our generator representation.

\litem{Initialize Generator Representation:} For each of the cells computed in the previous step, we set the anchor vertex and generator vector components to their corresponding grid cell dimension. In other words, we constrain the parallelotope to be contained within the cell through the generator representation. Formally speaking, suppose we have a grid cell $G$ in $n$-dimensional real vector space $\reals^n$ of the form $G = [l_1,u_1] \times [l_2, u_2] \times \cdots [l_n \times u_n]$. To constrain our parallelotope $P = \langle a, g_1, \cdots, g_n\rangle$ to be contained within $g$, it suffices to set the component variables such that $a, g_1, \cdots, g_n \in G$. For example, to set $a \in G$, the constraints should be initialized as below:
\begin{align}
\label{eq:gen_var_interval}
  a_1 \gets [l_1,u_1] & & a_2 \gets [l_2, u_2] & & \cdots & & a_n \gets [l_n,u_n]
\end{align}
%
%\begin{align*}
%  a_1 & \in [l_1,u_1] & a_1 & \in [l_2, u_2] & \cdots & & a_n \in [l_n,u_n] \\
%  g_{11} & \in [l_1,u_1] & g_{12} & \in [l_2, u_2] & \cdots&   & g_{1n} \in [l_n,u_n] \\
%  & \vdots & & \vdots &
%\end{align*}
%
In Algorithm \ref{alg:bern_prune}, the procedure responsible returning this assignment is $\ComputeGridRep$.

\litem{Perform the Functional Composition:} As stated in Equation \ref{eq:maxalpha}, the non-linear optimization predicate should be $\Lambda_i\cdot f$ for fixed template direction $\Lambda_i$. Under the assignments of the variables according to Equation \ref{eq:gen_var_interval} and interval arithmetic, we have the polynomial $\Lambda_i\cdot(f \circ T_p)$ where the coefficients are \emph{intervals} rather than real values.

\litem{Compute Bernstein Coefficient Intervals:} Now with our computed polynomial with interval coefficients, we can compute the Bernstein coefficient intervals using the formula displayed in Equation \ref{eq:bernstein_coeff}. By our initialization scheme above, this computation will yield intervals such that the Bernstein coefficients computed from any parallelotope contained in grid cell $P \subseteq G$ should lie within their respective coefficient intervals. Let $\{\barb_{\boldi}\}_{\boldi \in I_{G,\Lambda_i}}$ be the set of computed coefficient intervals where $I_{G,\Lambda_i}$ is an index of degrees which depend on the grid cell $G$ and template direction $\Lambda_i$. For the sake of clarity, we shall just denote this index set as $I$.

\litem{Find the Maximum/Minimum Interval:} Using $\{\barb_{\boldi}\}$, we find the maximum and minimum interval by simply finding the interval which has the largest upper-bound and the interval which has the smallest lower-bound. If $\barb_{\boldi} = [l_\boldi, u_\boldi]$, then
%
\begin{align}
  \mathfrak{I}_{G,\Lambda_i, \max} & = \argmax_{\boldi \in I} u_\boldi \\
  \mathfrak{I}_{G,\Lambda_i, \min} & = \argmin_{\boldi \in I} u_\boldi
\end{align}
%
Note that $\mathfrak{I}_{\max}, \mathfrak{I}_{\min}$ are the degrees of the Bernstein basis monomials whose intervals dominate the others. Additionally, we add all the intervals which overlap with the maximum and minimum intervals:
%
\begin{align}
  \begin{split}
      m_{G,\Lambda_i,\max} & = \{\boldi \in I ~|~ \barb_{\boldi} \cap \barb_{\mathfrak{I}_{\max}} \neq \emptyset \}\\
      m_{G,\Lambda_i,\min} & = \{\boldi \in I ~|~ \barb_{\boldi} \cap \barb_{\mathfrak{I}_{\min}} \neq \emptyset \}
  \end{split}
\end{align}

\litem{Store into Lookup Table:} The maximum and minimum intervals and their associated degrees are stored into a lookup table indiced by each grid cell and template direction $\Lambda_i$ in $\Lambda$.
\end{enumerate}

@@

  \begin{tabular}{|c|c|c|c|}
  \hline
  Model & Domain & Initial Set & \# of Grid Cells \\
  \hline
  Vanderpol & $[-3, 3] \times [-3, 3]$ & $[0.001, 0.005]\times [1.995, 2]$ & 1600 \\
  %\hline
  %SIR & $[0, 1]^3$ & $[0.799,0.8] \times [0.199,0.2] \times 0$ & 100 \\
  \hline
  \end{tabular}
\end{itemize}

During the course of experimentation, several observations hinting towards major obstacles hindering any trivial speed-up have been discovered for the two benchmark models. We list those obstacles below.

\subsection{Discrepancy of Degrees}
\label{sec:deg_disc}
This issue arises when we determine the maximum and minimum intervals and their associated monomials during the pre-computation step. We will demonstrate this phenomenon with the Vanderpol system.

Recall that the generator representation for a parallelotope $P$ would yield the linear transformation $T_P:[0,1] \rightarrow P$ which looks like $$ T_P(x,y) = q + g_0\cdot x + g_1\cdot y$$ for an anchor (base) vertex $q$ and two generator vectors $g_0,g_1$.
%
The composition with the generator representation would be tantamount to substituting the symbolic expressions as follows:
%
\begin{align} x & \leftarrow q_0 + g_{00}\cdot x + g_{01}\cdot y \\  y & \leftarrow q_1 + g_{01}\cdot x + g_{11}\cdot y\end{align}
%
The components of the composed mapping $f \circ T$ will individually look like:
%
\begin{align} (f \circ T)_0 & = q_1 + g_{01}\cdot x + g_{11}\cdot y \\ (f \circ T)_1 & = (1 - (q_0 + g_{00}\cdot x + g_{01}\cdot y)^2) * (q_1 + g_{01}\cdot x + g_{11}\cdot y) - (q_0 + g_{00}\cdot x + g_{01}\cdot y) \end{align}

If you inspect the polynomial $(f \circ T)_1$, the square times another linear factor of $x,y$ gives us a polynomial of degree $(3,3)$.
%
Suppose we calculate the non-linear optimization objective function as: $\Lambda_i \cdot (f \circ T_P)$ where we set $\Lambda_i = [0,1]^T$ (i.e the y-axis aligned vector), then the polynomial will be precisely be $(f \circ T)_1$, which has degree $(3,3)$.

However, the following occurs during the reachability algorithm: the actual polynomial computed for template direction $\Lambda_i =[0,1]^T$, that is the polynomial computed naturally during the parallelotope reachability algorithm, actually has lower degree than $(3,3)$.
%
Furthermore, the maximum and/or minimum degrees pre-computed actually of \emph{higher degree} than the degree of the actual polynomial computed during the procession of the algorithm. This would mean that the pre-computed degrees and their coefficient would never show up in the Bernstein expansion of the actual polynomial. To see this, recall Property \ref{prop:bern_basis}.

Consider the output presented in Figure \ref{fig:bern_prune_deg_output} computed with just the axis-aligned parallelotope over the VanderPol model with a grid parition of $40 \times 40$. We run the algorithm for one step and display the output during the optimization procedure for template direction $\Lambda_i = [0,1]^T$.
%-------------------------
\input{bern_prune_deg_output}
%-------------------------
In the first step above, the maximum degree is a lone monomial:
%
\begin{verbatim}
Returned set of Maximum Monom from Lookup Table:
[((3, 3), 2.18359741950000)]
\end{verbatim}
%
This means that the actual monomial with the maximum Bernstein coefficient:
\begin{verbatim}
Actual Max Monom Deg: (2, 0)
\end{verbatim}
%
was actually pruned out during the pre-computation phase.
%
What seems to happen quite frequently is the maximum or minimum intervals and their associated overlaps dominates the degree of the actual polynomial computed after composition during the reachability computation. To see this, note the anchor and generator vectors computed for the generator representation:
%
\begin{verbatim}
BASE VERTEX: [0.005, 2.0]
GENERATORS: [[-0.004, 0.0], [0.0, -0.0049999999999999]]
\end{verbatim}

The generators are axis-aligned, meaning that several degrees are annihilated during the composition $\Lambda_i\cdot (f\circ T_P)$. Hence, during our pre-computation step two, we consider a more general set of monomial degrees which may not reflect the relevant degree statistics found during the actual computation phase.

@@

To recapitulate, it appears that pre-computing the Bernstein coefficients and the subsequent analysis on their outputted intervals can overly skew the effect of ``non-relevant coefficients". These coefficients can only be pruned once the generator representation of the specific parallelotope is computed and the exact degree of the composed polynomial is determined.

\subsection{Contributions of Many Overlapping Cells}
Another obstacle stems from the observation that parallelotopes which have great overlap with many grid cells yield the full list of Bernstein coefficients. Hence, there is no speed-up gained in these cases. Consider the output displayed in Figure \ref{fig:bern_prune_wrapping_output} for step four.
%-------------------------
\input{bern_prune_wrapping_error}
%-------------------------
The main point to take here are the printed values of returned set of monomials from the lookup table:
%
\begin{verbatim}
Returned set of Maximum Monom from lookup_table:
 [((0, 1), 2.48598940176842),
 ((1, 2), 2.13075300161303),
 ((2, 1), 2.49645813555339),
 ...
 ((3, 3), 1.77817608667862)]
\end{verbatim}
%
From Step 4 onwards, the lookup table returns the full list of monomials of degree less than $(3,3)$ i.e all the relevant monomials during the pre-computation stage.
%
We tested this even for reachability computations lasting more than five steps. The full set of Bernstein coefficients are always returned after a certain step. For the Vanderpol model initialized with our parameters, this point would be around step $4$ or $5$.

As the wrapping error becomes worse, so does the utility of our lookup table. A guess is that as the conservativeness of our reachable becomes greater, it overlaps with more cells of the domain. This results in an cascading effect where the reachability algorithm is required to take into account more and more monomials as it progresses.

We speculate that the utility of our pruning method hinges on the careful control of the reachable set error. If the error becomes too great, we end of computing all of the coefficients, negating any benefits of a speed-up.

### 2022-07-30 thesis/staticalg.tex
Second draft of thesis finished

Equation~\ref{eq:maxalpha} is a form of $\mathsf{optBox(\Lambda_{i} \cdot f)}$ over $[0,1]^n$.
%
One can compute an upper-bound to this non-linear optimization by computing the Bernstein coefficients of $\Lambda_i \cdot f(a + \Sigma_{i=1}^{n} \alpha_i g_i)$ and taking the maximum and minimum coefficients as shown in Property~\ref{prop:bern_enclosure}.
%
Similarly, we compute the lower-bound of $\Lambda_{i}\cdot f(x)$ for all $x \in P$ by computing the upperbound of $-1 \times \Lambda_{i}\cdot f(x)$.
%

We iterate this process (i.e., computing the upper and lower bound of $\Lambda^Q_{i}\cdot f(x)$) for each parallelotope in the bundle $Q$ according to Equation \ref{eq:max_over_ptopes} and Equation \ref{eq:min_over_ptopes}).
%
% Observe that the role of the parallelotopes in the bundle is to compute an upper bound on the maximum value of $T_{i}f(x)$ by expanding the domain from $Q$ to the corresponding parallelotope $P$.
%
Therefore, the tightest upper bound on $\Lambda^Q_{i}\cdot f(x)$ over $Q$ is the least of the upper bounds computed from each of the parallelotopes.
%
A similar argument holds for lower bounds of $\Lambda^Q_{i}\cdot f(x)$ over $Q$.
%
\begin{figure}
\subfloat[A single ptope]{
  \begin{tikzpicture}
    \draw (0,0) -- (-1,2) -- (3,2) -- (4,0) -- cycle;
    \node at (1.5,1) {$P$};
    \draw[->, very thick] (5,1) -- (7,1) node[above, midway] {$f$};
    \draw (10,0) .. controls (7,1) ..(9,2) .. controls (10, 1).. (11,2) .. controls (14,1) .. (14,0) .. controls (11,-1) .. cycle;
    \node at (11,0.75) {$f(P)$};
  \end{tikzpicture}

}

\caption{Diagrams for the effect of the non-linear optimization procedure.}
\end{figure}
%
Therefore, the image of the bundle $Q$ will be the bundle $Q'$ where the upper and lower bounds for templates directions are obtained by solving a series of non-linear optimization problems of the form presented in Equation~\ref{eq:maxf}.

>>>>

Equation~\ref{eq:maxalpha} is a form of $\mathsf{optBox(\Lambda_{i} \cdot f)}$ over $[0,1]^n$.
%
One can compute an upper-bound to this non-linear optimization by computing the Bernstein coefficients of $\Lambda_i \cdot f(a + \Sigma_{i=1}^{n} \alpha_i g_i)$ and taking the maximum and minimum coefficients as shown in Property~\ref{prop:bern_enclosure}.
%
Similarly, we compute the lower-bound of $\Lambda_{i}\cdot f(x)$ for all $x \in P$ by computing the upper-bound of $-1 \times \Lambda_{i}\cdot f(x)$.
%
\begin{remark}
The original algorithm using Bernstein expansion proposed by \cite{dreossi2016parallelotope} assumed polynomial dynamics i.e $f$ is polynomial in the system variables.
%
This is to ensure that a $\Lambda_{i}\cdot f(x)$ is a polynomial after the composition shown in Equation \ref{eq:maxalpha}. Proper Bernstein expansion of this polynomial allows us to exploit the enclosure property of Bernstein coefficients. However, the use of other non-linear optimization solvers, such as Kodiak \cite{kodiak}, allows us to use more general dynamics involving trigonometric and root functions. A Taylor expansion of any analytic function can also be truncated to some suffciently large degree to admit a power series expansion.
\end{remark}

We iterate this process (i.e., computing the upper and lower bound of $\Lambda^Q_{i}\cdot f(x)$) for each parallelotope in the bundle $Q$ according to Equation \ref{eq:max_over_ptopes} and Equation \ref{eq:min_over_ptopes}).
%
% Observe that the role of the parallelotopes in the bundle is to compute an upper bound on the maximum value of $T_{i}f(x)$ by expanding the domain from $Q$ to the corresponding parallelotope $P$.
%
Therefore, the tightest upper bound on $\Lambda^Q_{i}\cdot f(x)$ over $Q$ is the least of the upper-bounds computed from each of the parallelotopes.
%
A similar argument holds for lower bounds of $\Lambda^Q_{i}\cdot f(x)$ over $Q$.
%
%\begin{figure}
%\subfloat[A single ptope]{
%  \begin{tikzpicture}
%    \draw (0,0) -- (-1,2) -- (3,2) -- (4,0) -- cycle;
%    \node at (1.5,1) {$P$};
%    \draw[->, very thick] (5,1) -- (7,1) node[above, midway] {$f$};
%    \draw (10,0) .. controls (7,1) ..(9,2) .. controls (10, 1).. (11,2) .. controls (14,1) .. (14,0) .. controls (11,-1) .. cycle;
%    \node at (11,0.75) {$f(P)$};
%  \end{tikzpicture}
%}
%\caption{Diagrams for the effect of the non-linear optimization procedure.}
%\end{figure}
%
Therefore, the image of the bundle $Q$ will be the bundle $Q'$ where the upper and lower-bounds for templates directions are obtained by solving a series of non-linear optimization problems of the form presented in Equation~\ref{eq:maxf}.
